---
title: "Omnipath for building Boolean Networks"
output: rmdformats::downcute
date: "2023-05-05"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	#echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```
```{r, include=FALSE}
setwd("/Users/sophia/Documents/MET_project/omnipath-r-pipeline")
```

# Building a network using Omnipath
Import interactions from Omnipath
```{r, include=TRUE}
#Import libraries
library(OmnipathR)
source("./omnipath_myfunctions.R")

#Interactions with references from omnipath
interactions <- import_all_interactions()
interactions <- with_references(interactions)
```


## Get interactions of a specific gene
**search_gene**: Returns database with all the interactions of the input gene, its sources and targets. Can be filtered by: "sources", "positive_sources", "negative_sources", "targets", "positive_targets", "negative_targets"
```{r, include=TRUE}
gene="GRHL2"
search_gene(gene, interactions)

gene="CDH1"
search_gene(gene, interactions, "negative_sources")
```


## Plot direct interactions of a gene
**plot_neighbours**:
```{r, include=TRUE}
plot_neighbours("GRHL2", interactions)
plot_neighbours("ZEB2", interactions, type = 1, "negative_sources")
```


## Get interactions for a set of genes
**get_gene_interaction**:
```{r, include=TRUE}
subset_nodes=c("GRHL2","ZEB1")
get_gene_interaction(subset_nodes, interactions)
```


## Plot direct interactions
Define genes to include in the network and plot direct interactions between the genes with **plot_direct**. Option type=1 to include interaction type in plot.
```{r, include=TRUE}
genes=c("GRHL2","ZEB1","hsa-miR-200c","TWIST1")
plot_direct(genes,interactions, type = 1)
```


## Plot direct and indirect interactions
Plot direct and direct interactions from a set of genes to another with **plot_paths**. Option type=1 to include interaction type in plot.
```{r, include=TRUE}
start=c("GRHL2","TP63")
end=c("ZEB1")
plot_paths(start,end,interactions)
```


## Make a boolean model with just direct interactions
```{r, include=TRUE}
save_bnet(genes,genes, interactions,"model_direct.bnet",include_indirect=FALSE)
read.csv("model_direct.bnet")
```


## Make a boolean model with direct and indirect interactions
```{r, include=TRUE}
#genes=c("GRHL2","ZEB1","hsa-miR-200c")
genes=c("GRHL2","ZEB1","hsa-miR-200c","TP63","CDH1","TWIST1")
save_bnet(genes,genes, interactions,"model_indirect.bnet",include_indirect=TRUE)
head(read.csv("model_indirect.bnet"))
```
